Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-20 chapters/mcmc/paper.tex
fix image layout
change title

%  \caption{Our approach leverages a geographic reference database (b)
%  to estimate the geo-location (c) of a query image (a). (b) Top scoring
%samples (red arrows) are close to the actual location (green dot).}

@@

Proportional to the probability distribution of the camera parameters,
$f(\Theta; \mathbf{C})$, the scoring function, $S(\Theta;
\mathbf{C})$, is defined as a linear combination of multiple constraint
functions:
%
\begin{equation}
  S(\Theta; \mathbf{C}) = \sum_{}{w_i g(c_i, \Theta)} \propto
  f(\Theta; \mathbf{C}),
\end{equation}
%
where $w_i$ is a weight and $g(c_i, \Theta)$ is a constraint function
which is larger if the calibration, $\Theta$, is more consistent with
the image information, $c_i$. While the exact set of constraints
depends on the image and database contents, we define a variety of
% scott review
functions in our implementation, including geometric configuration of
multiple weak correspondences, constraints on geographic location, and
priors over the
%
field of view and camera orientation. We focus on the first
constraint, the latter are simple Gaussian and uniform distributions.

>>>>

@@

Proportional to the probability distribution of the camera parameters,
$f(\Theta; \mathbf{C})$, the scoring function, $S(\Theta;
\mathbf{C})$, is defined as a linear combination of multiple constraint
functions:
%
\begin{equation}
  S(\Theta; \mathbf{C}) = \sum_{}{w_i g(c_i, \Theta)} \propto
  f(\Theta; \mathbf{C}),
\end{equation}
%
where $w_i$ is a weight and $g(c_i, \Theta)$ is a constraint function
which is larger if the calibration, $\Theta$, is more consistent with
the image information, $c_i$. While the exact set of constraints
depends on the image and database contents, we define a variety of
% scott review
functions in our implementation, including geometric configuration of
multiple weak correspondences, constraints on geographic location, and
priors over the field of view and camera orientation. 
%
We focus on the first
constraint, the latter are simple Gaussian and uniform distributions.
